Demes: a standard format for demographic models

### 2022-04-22 fig/minted-snippet.tex

\begin{minted}[numbersep=5pt]{python}
import demes, msprime, moments
# load the demographic model and specify sample sizes
model = demes.load("tennessen.yml")
samples = {"AFR": 20, "EUR": 20}
# import model as msprime demography and simulate ancestry
demography = msprime.Demography.from_demes(model)
ts = msprime.sim_ancestry(
    [msprime.SampleSet(n, ploidy=1, population=p) for p, n in samples.items()],
    demography=demography)
# compute the expected joint SFS using moments
sfs = moments.Spectrum.from_demes(model, samples=samples)
\end{minted}

>>>>

\begin{minted}[numbersep=5pt]{python}
import demes, msprime, moments
# load the demographic model and specify sample sizes
model = demes.load("tennessen.yaml")
samples = {"AFR": 20, "EUR": 20}
# import model as msprime demography and simulate ancestry
demography = msprime.Demography.from_demes(model)
ts = msprime.sim_ancestry(
    [msprime.SampleSet(n, ploidy=1, population=p) for p, n in samples.items()],
    demography=demography)
# compute the expected joint SFS using moments
sfs = moments.Spectrum.from_demes(model, samples=samples)
\end{minted}
